---
title: "What link can we make between nutriscore grade (A,B,C,D,E) and nutritional values for the products 'en:poultry' in France ?"
output:
  pdf_document: default
  word_document:
    toc: yes
  html_document:
    toc: yes
    always_allow_html: true
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
library(dplyr)
library(ggplot2)
library(readr)

drouichi <- read.delim("drouichi.csv", sep = "\t")

data_poultry <- drouichi %>%
  filter(grepl("en:french-poultry", labels_tags)) %>%
  select(everything())

```

Main objective : Present to English consumers consistant data about the
link between french products and nutriscore grade to make them inform
better than before.

What is the nutriscore ? : The nutriscore is a grade system with letters
and colors, starting to A and dark green and finishing by E and red,
trying to inform consumers when they buy a product about the nutritional
value of it. More the letter is closer to A and more the product can be
considered healthy.

Which products will I study ? : The products I'm studying are on the
family "en:poultry" in France.

How many observations do I have ? : 
9345 observations of 27 variables at the start. 
3297 observations of 27 variables with the "en:french-poultry" constraint.

Organization of this document : The rest of this document contains 4 bar
chart and 1 table chart. Each graphic has an analysis and interpretation
below them.

First graphic : This is a bar chart presents the average quantity of
sugar on the y axis according to each nutriscore per 100 g of
'en:poultry' products" on the x axis.

```{r, echo=FALSE}
sugars_100g <- as.numeric(as.character(drouichi$sugars_100g))

moyenne_sugars <- data_poultry %>%
  group_by(nutriscore_grade) %>%
  summarize(Moyenne_Sugars = mean(sugars_100g, na.rm = TRUE))

hauteurs <- moyenne_sugars$Moyenne_Sugars

# Couleurs spécifiques pour chaque barre
couleurs <- c("darkgreen", "green", "yellow", "orange", "red")

# Créer un histogramme avec des couleurs spécifiques
barplot(hauteurs, 
           names.arg = c("A","B","C","D","E"),
        xlab = "Nutriscore Grade",
        ylab = "Sugars (per 100g)",
        main = "Average quantity of sugar for each nutriscore per 100 g of products",
        col = couleurs)

```

The average quantity of sugar for the products "en:poultry" in France is
pretty weak except for the products with the E nutriscore. In average,
the products with the E nutriscore contain 3 times more sugar than the
products with the D nutriscore to reach above 3 grams of sugar for 100
grams of product. More the nutriscore is worse and more the products
have a chance to contain more sugar.

Second graphic : This is a bar chart presents the average quantity of
salt on the y axis according to each nutriscore per 100 g of
'en:poultry' products" on the x axis.

```{r, echo=FALSE}
salt_100g <- as.numeric(as.character(drouichi$salt_100g))

moyenne_salt <- data_poultry %>%
  group_by(nutriscore_grade) %>%
  summarize(Moyenne_Salt = mean(salt_100g, na.rm = TRUE))

hauteurs <- moyenne_salt$Moyenne_Salt

# Couleurs spécifiques pour chaque barre
couleurs <- c("darkgreen", "green", "yellow", "orange", "red")

# Créer un histogramme avec des couleurs spécifiques
barplot(hauteurs, 
           names.arg = c("A","B","C","D","E"),
        xlab = "Nutriscore Grade",
        ylab = "Salt (per 100g)",
        main = "Average quantity of salt for each nutriscore per 100 g of products",
        col = couleurs)

```

The average quantity of salt is pretty high except for the products with
the A nutriscore. The products with the B nutriscore have almost 4 times
more salt than those with the A nutriscore and those with the D
nutriscore contain 2 times more salt than those with the B nutriscore.
The products with the C nutriscore are between both.

On top of that, we can say the products "en:poultry" in France are more
salted than sugared in general.

Third graphic : This is a bar chart presents the average quantity of fat
on the y axis according to each nutriscore per 100 g of 'en:poultry'
products" on the x axis.

```{r, echo=FALSE}
fat_100g <- as.numeric(as.character(drouichi$fat_100g))

moyenne_gras <- data_poultry %>%
  group_by(nutriscore_grade) %>%
  summarize(Moyenne_Gras = mean(fat_100g, na.rm = TRUE))

hauteurs <- moyenne_gras$Moyenne_Gras

# Couleurs spécifiques pour chaque barre
couleurs <- c("darkgreen", "green", "yellow", "orange", "red")

# Créer un histogramme avec des couleurs spécifiques
barplot(hauteurs, 
           names.arg = c("A","B","C","D","E"),
        xlab = "Nutriscore Grade",
        ylab = "fat (per 100g)",
        main = "Average quantity of fat for each nutriscore per 100 g of products",
        col = couleurs)

```

The average quantity of fat is really high in general. In average, only
The products with the A nutriscore have a weak average quantity of fat
because these are 2 times less fat than products with the B nutriscore.
The other products contain between under 10 grams to 15 grams of fat per
100 grams of product except the products with the E nutriscore which
reach beyond 25 grams of fat per 100 grams of product in average.

On top of that, we can say the products "en:poultry" in France are
really more fat than sugared and salted.

Last graphic : This is a bar chart presents the average quantity of
proteins on the y axis according to each nutriscore per 100 g of
'en:poultry' products" on the x axis.

```{r, echo=FALSE}

proteins_100g <- as.numeric(as.character(drouichi$proteins_100g))

moyenne_prot <- data_poultry %>%
  group_by(nutriscore_grade) %>%
  summarize(Moyenne_Proteines = mean(proteins_100g, na.rm = TRUE))

hauteurs <- moyenne_prot$Moyenne_Proteines



# Couleurs spécifiques pour chaque barre
couleurs <- c("darkgreen", "green", "yellow", "orange", "red")

# Créer un histogramme avec des couleurs spécifiques
barplot(hauteurs, 
           names.arg = c("A","B","C","D","E"),
        xlab = "Nutriscore Grade",
        ylab = "Proteins (per 100g)",
        main = "Average quantity of proteins for each nutriscore per 100 g of products",
        col = couleurs)

```

The products "en:poultry" in France are really proteined. In average,
all products contain at least more than 15 grams proteins per 100 grams
of product. The products with the A nutriscore have beyond 20 grams of
proteins and they are the only one in this case. The B and C nutriscore
contain the same average of proteins on their products to reach almost
20 grams of proteins per 100 grams. The products with the D and E
nutriscore have a little bit less proteins than the products with a
better nutriscore.

The table : This is a table presents the average quantity of fat on the
y axis according to each nutriscore per 100 g of 'en:poultry' products"
on the x axis.

```{r, echo=FALSE}

library(knitr)
library(dplyr)


nutriscore_grade <- factor(drouichi$nutriscore_grade)

# Compter le nombre de produits pour chaque Nutriscore
proportions_nutriscore <- data_poultry %>%
  group_by(nutriscore_grade) %>%
  summarize(Proportion = n() / nrow(data_poultry)*100)%>%
  rename(Nutriscore_grade = nutriscore_grade) %>% # Renommer temporairement le champ pour l'affichage
  rename(`Proportion (in%)` = Proportion) %>% # Renommer la colonne des proportions
  mutate(`Proportion (in%)` = round(`Proportion (in%)`, 1)) # Arrondir à 1 chiffre après la virgule


# Afficher le tableau avec les proportions des produits pour chaque Nutriscore
kable(proportions_nutriscore, caption = "Proportion of products for each nutriscore grade")


```

This table shows that over 40% of products has the A nutriscore and 48%
of these represent the B and C nutriscore. Moreover, less than 1% of
products gets the E nutriscore. We might say the majority of
"en;poultry" products are healthy.

To conclude, the products of the family "en:poultry" in France are more
proteined and fat than salted and sugared. We can notice with all these
graphics that the products with E nutriscore have a high average for all
of them so we may say the E nutriscore products have bad nutritional
values in all case but these products represent less than 1% of
"en:poultry" product, combined with D nutriscore products, it always
represents less than 10% of products in total. We can understand the
"en:poultry" products in France are probably a proteined range of
product with the majority of these products have at least the C
nutriscore.
